A Review of Lossless Data Compression Methods

### 2018-11-16 paper.tex
Add first information about LZW.

\title{A Review of Lossless Data Compression Methods}
\author{Anonymous}

@@

This result places a lower bound on the \emph{efficiency} of prefix
codes in general, and suggests the sorts of data which are less
compressable, and even uncompressable (since such an input must
exist!) Since entropy of some channel $X$ with an alphabet $C$ is
defined to be $H(X) = -\sum_{c \in C} P(c)\log_2{c}$, we can
illustrate the implications of this result with a simple
example. Suppose we are attempting to compress a particular channel
$X$ which is text document in which the frequencies of every letter of
the Latin alphabet are distributed equally. (It is extremely unlikely
that a text in any human language would have this property; it is used
here to illustrate a pathological edge case in general.) Then the
average word length must be greater than
$26 * -\frac{1}{26} \log_2{\frac{1}{26}} \approx 4.7$ bits. If we were
to construct a naive code to encode the Latin alphabet, for instance
$A=1, B=2,...$, we would require 5 bits for each letter. Shannon's
Noiseless Coding Theorem says this is more or less as good as we can
do, so for this case it is very difficult to actually compress our
input. Consider another document in which case one letter, let's say
$E$, occurs significantly more often than the others, for instance
$\frac{27}{52}$ of the time, relative to $\frac{1}{52}$ for every
other letter. Then by Shannon's Noiseless Coding Theorem, it is
possible to construct a code with an average word length greater than
$25 * -\frac{1}{52} \log_2{\frac{1}{52}} - \frac{27}{52}
\log_2{\frac{27}{25}} \approx 3.2$, meaning that we can compress such
this document approximately $33\%$ more efficiently than the uniform
one. This situation is somewhat contrived, but it serves to illustrate
the fundamental limits of prefix codes in general.

@@

The Lempel-Ziv compression algorithm, commonly referred to as LZ for
short, is one of the most widespread compression schemes in use,
especially when including its large family of derivative methods. It
was first introduced in 1977. \cite{LempelZiv} Algorithms based on
the Lempel-Ziv algorithms are very efficient and work well with a wide
variety of inputs.

@@

Since knowing the structure of a given input can allow the
construction of a more efficient data compression scheme, it is
worthwhile to study some compression scheme which is specifically
designed to store a particular type of data. In this section I will
describe the structure and function of the Free Lossless Audio Codec,
known more commonly by its acronym FLAC, a popular format for
high-fidelity audio storage.

>>>>

\title{A Review of Lossless Data Compression Methods}
\author{Blargh}

@@

This result places a lower bound on the \emph{efficiency} of prefix
codes in general, and suggests the sorts of data which are less
compressable, and even uncompressable (since such an input must
exist!) Since entropy of some channel $X$ with an alphabet $C$ is
defined to be $H(X) = -\sum_{c \in C} P(c)\log_2{c}$, we can
illustrate the implications of this result with a simple
example. Suppose we are attempting to compress a particular channel
$X$ which is text document in which the frequencies of every letter of
the Latin alphabet are distributed equally. (It is extremely unlikely
that a text in any human language would have this property; it is used
here to illustrate a pathological edge case in general.) Then the
average word length must be greater than
$26 * -\frac{1}{26} \log_2{\frac{1}{26}} \approx 4.7$ bits. If we were
to construct a naïve code to encode the Latin alphabet, for instance
$A=1, B=2,...$, we would require 5 bits for each letter. Shannon's
Noiseless Coding Theorem says this is more or less as good as we can
do, so for this case it is very difficult to actually compress our
input. Consider another document in which case one letter, let's say
$E$, occurs significantly more often than the others, for instance
$\frac{27}{52}$ of the time, relative to $\frac{1}{52}$ for every
other letter. Then by Shannon's Noiseless Coding Theorem, it is
possible to construct a prefix code with an average word length
greater than
$25 * -\frac{1}{52} \log_2{\frac{1}{52}} - \frac{27}{52}
\log_2{\frac{27}{25}} \approx 3.2$, meaning that we can compress such
this document approximately $33\%$ more efficiently than the uniform
one. This situation is somewhat contrived, but it serves to illustrate
the fundamental limits of prefix codes in general.

Prefix codes on their own are extremely useful in communication
applications, but their true power is revealed when used as a building
block within more powerful, sophisticated compression schemes.

@@

The Lempel-Ziv compression algorithm, commonly referred to as LZ77 or
LZ78 for short, is one of the most widespread compression schemes in
use, especially when including its large family of derivative
methods. It was first introduced in 1977. \cite{LempelZiv} Algorithms
based on the Lempel-Ziv algorithms are relatively efficient and work
well with a wide variety of inputs.

The algorithm is based on a dictionary-style approach; that is to say,
it creates a dictionary of codewords within the input bit-string
as the algorithm progresses.

\subsection{Lempel-Ziv-Welch}

The Lempel-Ziv-Welch compression algorithm was an extension of the
Lempel-Ziv algorithm which was introduced soon after the publication
of the original LZ77. \cite{LempelZivWelch}

@@

Since knowing the structure of a given input can allow the
construction of a more efficient data compression scheme, it is
worthwhile to study some compression scheme which is specifically
designed to store a particular type of data. In this secion I will
describe the structure and function of the Free Lossless Audio Codec,
known more commonly by its acronym FLAC, a popular format for
high-fidelity audio storage.
